---
title: "GGPLOT visualizations"
author: "Jothi Prakash"
date: "18 February 2018"
output: html_document
---

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
# Install necessary packages
packages <- c("ggplot2",
              "plotly",
              "dplyr")
lapply(X = packages,
       FUN = require,
       character.only = T)
```

# Scatter Plot

The most frequently used plot for data analysis is undoubtedly the scatterplot. Whenever you want to understand the nature of relationship between two variables, invariably the first choice is the scatterplot.

It can be drawn using `geom_point()`. Additionally, `geom_smooth` which draws a smoothing line (based on loess) by default, can be tweaked to draw the line of best fit by setting `method='lm'`.

```{r}
options(scipen = 999) # Turn-off scientific notation like 1e+18
theme_set(theme_bw()) # Preset the bw theme
data("midwest",
     package = "ggplot2")

# Scatterplot
gg <- ggplot(midwest, aes(x = area, y = poptotal)) +
  geom_point(aes(col = state, size = popdensity)) +
  geom_smooth(method = "loess", se = F) +
  xlim(c(0, 0.1)) +
  ylim(c(0, 500000)) +
  labs(subtitle = "Area vs Population",
       y = "Population",
       x = "Area",
       title = "Scatter Plot",
       caption = "Source: midwest")
ggplotly(gg)
```